Missing the Point: Non-Convergence in Iterative Imputation Algorithms

### 2020-05-04 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Add requirements thesis submission

---
title: "Missing the Point: Non-Convergence in Iterative Imputation Algorithms"
runninghead: Oberman
author:
  name: H. I. Oberman
  num: 1
address:
  num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Iterative imputation is a popular tool to accommodate missing data. While it is widely accepted that valid inferences can be obtained with this technique, these inferences all rely on algorithmic convergence. There is no consensus on how to evaluate the convergence properties of the method. This paper provides insight into identifying non-convergence of iterative impuation algorithms."
keywords: missing data, iterative imputation, non-convergence, mice
classoption:
 - Royal
 - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
 rticles::sage_article:
  keep_tex: yes
---

@@

**[Add to this section: 1) emphasize that the iterations in the plots are averages across repetitions, not within one run of MICE; 2) sample effects due to single complete dataset?? 3) Add more info about figure legends and axes.]**
Primarily, we want to know what the effect is of inducing non-convergence on the estimated $Q$s. Specifically, we are interested in the bias of $\bar{Q}$ for all $Q$s and the confidence validity of $\bar{Q}$ for $Q=\beta$. Therefore, we plot these performance measures against the simulation conditions (the number of iterations $T$ and the missingness proportion $p_{mis}$). We look at averages across simulation repetitions.

>>>>

---
title: "Missing the Point: Non-Convergence in Iterative Imputation Algorithms"
runninghead: Oberman
author:
  name: H. I. Oberman
  num: 1
address:
  num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Iterative imputation is a popular tool to accommodate missing data. While it is widely accepted that valid inferences can be obtained with this technique, these inferences all rely on algorithmic convergence. There is no consensus on how to evaluate the convergence properties of the method. This paper provides insight into identifying non-convergence of iterative impuation algorithms."
keywords: missing data, iterative imputation, non-convergence, mice
classoption:
 - Royal
 - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    # includes:
    #   in_header: preamble.tex
    keep_tex: yes
    base_format: rticles::sage_article
---

@@

**[Add to this section: 1) emphasize that the iterations in the plots are averages across repetitions, not within one run of MICE; 2) sample effects due to single complete dataset?? 3) Add more info about figure legends and axes 4) the ac and rhat are independent of missingness, not the thetas.]**
Primarily, we want to know what the effect is of inducing non-convergence on the estimated $Q$s. Specifically, we are interested in the bias of $\bar{Q}$ for all $Q$s and the confidence validity of $\bar{Q}$ for $Q=\beta$. Therefore, we plot these performance measures against the simulation conditions (the number of iterations $T$ and the missingness proportion $p_{mis}$). We look at averages across simulation repetitions.

### 2020-05-04 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Add requirements thesis submission

\textbf{{[}Add to this section: 1) emphasize that the iterations in the
plots are averages across repetitions, not within one run of MICE; 2)
sample effects due to single complete dataset?? 3) Add more info about
figure legends and axes.{]}} Primarily, we want to know what the effect
is of inducing non-convergence on the estimated \(Q\)s. Specifically, we
are interested in the bias of \(\bar{Q}\) for all \(Q\)s and the
confidence validity of \(\bar{Q}\) for \(Q=\beta\). Therefore, we plot
these performance measures against the simulation conditions (the number
of iterations \(T\) and the missingness proportion \(p_{mis}\)). We look
at averages across simulation repetitions.

>>>>

\textbf{{[}Add to this section: 1) emphasize that the iterations in the plots are averages across repetitions, not within one run of MICE; 2) sample effects due to single complete dataset?? 3) Add more info about figure legends and axes 4) the ac and rhat are independent of missingness, not the thetas.{]}}
Primarily, we want to know what the effect is of inducing non-convergence on the estimated \(Q\)s. Specifically, we are interested in the bias of \(\bar{Q}\) for all \(Q\)s and the confidence validity of \(\bar{Q}\) for \(Q=\beta\). Therefore, we plot these performance measures against the simulation conditions (the number of iterations \(T\) and the missingness proportion \(p_{mis}\)). We look at averages across simulation repetitions.
